Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-05-31 paper/main.tex
add feedback of review before introduction

>>>>

\todo[inline]{\textbf{My notes:}\par
    1. change url(s) of datasets\par
    2. individual ROIs in the manuscript are NOT the ``masks'' but thresholded
    t-maps that were later ``titrated'' individually to get the mask\par
    -> imo it's better to adjust the figures (needs some coding though) than
    changing the text; I hope some significant voxels will still be visible in
    all subjects that have significant voxels)\par
    individual thresholds: s. studyforrest-data-visualrois/code/stats2rois.cfg
}

\todo[inline]{email from Barbara Cheifet (Consultant Editor):
    \textbf{Guidelines}\par

    - provide your revised manuscript as either a Word or LaTeX document, with
    separate figure files.\par

    - submit revision here: https://mts-scidata.nature.com/\par

    - replace "subjects" with "participants" throughout the paper.\par

    - split "Code and Data availability" into two sections.\par

    - there isn't a link to the OpenNeuro dataset in the paper, please include
    this, as it seems relevant\par

    - \underline{provide detailed point-by-point response to the referees'
    comments}, describing how you have addressed their concerns, with your
    revised manuscript.

    - ensure your manuscript complies with our format requirements:\par
    https://www.nature.com/sdata/publish/submission-guideline

    - ensure that your references conform fully to the Nature style;
    examples:\par
    http://www.nature.com/sdata/publish/submission-guidelines\#refs

    - replace your initial-submission image files with production quality
    figures. Line-art figures should be provided in a suitable vector-graphic
    format, ideally by saving them directly in the EPS or PDF formats from the
    program used to create them.

    - figures should not include Figure number labels in the image:\par
    https://www.nature.com/sdata/publish/submission-guidelines\#figures

    - remove the supplementary material from main manuscript text;
    supply it as a separate PDF.

    - remove the keywords from your manuscript text.

    - ensure a clear open data license (e.g. CC0 or CC BY) appears on your
    OpenNeuro record landing page

    - add an Author Contributions section after the Acknowledgements.

    - ensure your manuscript sections are provided in the following order:
    Abstract, Introduction, Results, Discussion, Methods, Data Availability,
    Code, Availability, References, Acknowledgements, Author Contributions \&
    Competing Interests\par

    - merge your data citations into your main 'References' section, as per our
    revised submission guidelines:\par
    https://www.nature.com/sdata/publish/submission-guidelines\#data\_citations
}

\todo[inline]{email from Barbara Cheifet (Consultant Editor):
    \textbf{RevisionChecklist}

In order to process your revised manuscript, we will require the following
items:

1) A cover letter describing your response to our editorial requests.

2) A point-by-point response to any issues raised by our referees.

3) revised version of your text as Word or TeX/LaTeX file with
\textbf{all changes highlighted; COH: how?}.

4) The final versions of any Supplementary Information files.

5) Publication quality figures in the TIFF, EPS, or PDF formats.

6) Final accession numbers or DOIs for any deposited datasets.

7) Any authors who have an ORCID and want it to appear on the final publication should add it to their account before you resubmit your revision. ORCIDs may not be added to our system after a paper has been accepted for publication.}

\todo[inline]{\textbf{Editorial Board Member}:\par
[\dots] reviewer 2 also believes that additional work is required to make this suitable for publication.
I believe that these are technically rather substantive amendments, but it is
possible that some of the required work has already been undertaken by your
team.

I am inviting you to revise the MS for further review (though probably
just to Reviewer 2). While you should pay particular attention to Reviewer 2's
feedback, I think it is important to attend to the points raised by Reviewer 1
which will improve the clarity of presentation.}

\todo[inline]{\textbf{Reviewer \#1}

minor suggestions for clarity that you might address or not:

\textbf{Introduction}\par

- The claim for what and where cites \underline{Goodale and Milner (1992)},
which is literally a call for what and how pathways. The function of these
pathways remains in dispute but \underline{its clear that where (spatial
processing) must take place in both streams.} You should probably
acknowledge that.

- This does not read well. It's a broken sentence: “Second, studies used a
block-design paradigm to maximize detection power.”

- suggest: “We investigate whether increased” not “we investigate if increased”

- I don’t understand this “because all three operationalization capitalize on”.
I think this must be a typo graphical error.

\textbf{Discussion}\par
- I am not sure I understand \underline{your use of immanent do you mean
inherent?} Or do you really mean something that is manifest in the pictures or
description. It's a low frequency that might need explaining: "Similarly, our
results suggest that the pPPA is more concerned with visual aspects immanent in
pictures or movie shots of landscapes. The aPPA might be more concerned with
non-visual aspects of spatial information (e.g. spatial contextual
information57) as immanent in both visual and verbal stimuli."

\textbf{Incidental results}\par
- I did not really understand this; you may want to elaborate/clarify what you
mean, perhaps with an example: "Increased activity in primary and secondary
auditory cortices could be attributed to changes in the soundscape that possibly
accompany the narrator when he is indicating the switch to another setting by
describing its identity or layout."}

\todo[inline]{\textbf{Reviewer \#2}

The results have been weakly presented (see major comment \#3). This comment
should be properly addressed in a revision.

\textbf{Major comments:}

1. \underline{in AV}, PPA has been identified based on the contrast of vse\_new
vs. vpe\_old. Although the activation matches with the area localized by the
block-design experiment, this contrast \underline{could have several potential
confounds}: At the transition to a new setting, \underline{pixel-level changes}
in the movie frames are usually higher, which could lead to non-specific
activations in visual cortex and in regions posterior to PPA.

Also it appears that some \underline{cognitive factors like novelty, surprise,
and attention} are not balanced in this contrast. Involvement of
\underline{memory} is another confounding factor - at least the contrasts of
vse\_new vs. vpe\_new and vse\_old vs. vpe\_old do not have this problem.
\underline{If the movie frames are annotated for things like} landscape,
building, face, people, body, tool, etc., a straightforward contrast could be
scenes vs. other categories (similar to a contrast used in the audio-description
movie experiment). It is not clear why the authors have not considered such
obvious contrast.

2. In addition to anterior PPA, auditory descriptions of scenes have activated a
*larger* cluster in \underline{RSC/Precuneus (Table 5)}. This is quite
interesting because these regions in medial parietal cortex are broadly involved
in semantic processing of scenes (see recent papers by \underline{Silson and
colleagues}).  Unfortunately, those \underline{activations are not clearly
visible in the selected slices shown in Figures 2 and 3}. This brings me to my
next comment.

3. Visualization of cortical maps in a volume format is not ideal. The
\underline{authors should show the activation maps on the surface} so that

a) the whole-brain activation pattern (e.g. in medial parietal, superior temporal, and lateral prefrontal regions) could be easily evaluated, and

b) the \underline{precise topography of activations in posterior PPA - anterior
PPA could be evaluated}.

The surface-based analysis/visualization of fMRI data
has also other advantages including a better smoothing that is constrained to
the cortical gray matter ribbon and a more optimized inter-subject averaging.

As far as I know, the structural data of studyforrest.org are processed in
Freesurfer, and the authors may already have reconstructed cortical surfaces of
subjects. Thus, the authors can project the individual-subject fMRI data to the
standard fsaverage surface, do minimal smoothing on surface (if needed), and
perform group-level surface-based registration and averaging (COH: goddamnit)

4. AO data have been collected in 7T scanner at the resolution of 1.4 mm
isotropic voxels, while the audio-visual movie data have been collected in 3T
scanner at the resolution of 3 mm isotropic voxels. During preprocessing, both
datasets have been transformed to a common template (2.5 mm isotropic voxels),
however, one dataset is down-sampled and the other one is up-sampled. Could
differences in data acquisition and voxel resolution be a concern here?

\textbf{Minor comments}:\par
Preprocessing, first paragraph, line 4: were dropped to -> were dropped

Event selection, last paragraph, line 5: compute -> computed

Hemodynamic modeling: what do you mean by the six participant regressor?

Results, first paragraph (and in two other instances): can found -> can be found

Control contrasts, first paragraph, line 2: finds -> findings
}
